---
title: "Stand Walk Recon Sheet"
output:
  html_document:
    css: style_1.css
params:
  stand_id:                         # string
  stand_polys:                      # sf
  age_pts:                          # sf
  fixed_pts:                        # sf
  prism_pts:                        # sf
  age_fixed_summary:                # data frame
  stand_summary:                    # data frame
  species_summary:                  # data frame
  health_summary:                   # data frame
---

```{r get_data, echo=FALSE, warning=FALSE}
report_version <- "0.1.5"

library(sf)
library(units)
library(dplyr)
library(stringr)
library(lubridate)
library(tidyr)

# Get the species-mast type table
fmg_dir <- ".."
fmg_data <- file.path(fmg_dir, "data")
spp_masttype_file <- file.path(fmg_data, "SppMastType.csv")
spp_masttype <- read.csv(spp_masttype_file)
```

```{r test_data, echo=FALSE}
# For testing (cannot use the variable name `params` as it is controlled by the IDE)
# params2 <- list("stand_id" = stand_id,
#                 "age_fixed_summary" = age_fixed_summary,
#                 "stand_summary" = stand_summary,
#                 'species_summary' = species_summary,
#                 "health_summary" = health_summary)
```

```{r select_stand, echo=FALSE}
# Determine if `stand_polys` are `Site` or `Stand`, then calculate filter for 
# current stand.
if("SID" %in% colnames(params$stand_polys)) {
  # FMG Stand
  age_pts_st   <- dplyr::filter(params$age_pts, 
                                SID == params$stand_id)
  fixed_pts_st <- dplyr::filter(params$fixed_pts, 
                                SID == params$stand_id)
  prism_pts_st <- dplyr::filter(params$prism_pts, 
                                SID == params$stand_id)
  age_fixed_st <- dplyr::filter(params$age_fixed_summary, 
                                SID == params$stand_id)
  stand_st     <- dplyr::filter(params$stand_summary, 
                                SID == params$stand_id)
  species_st   <- dplyr::filter(params$species_summary, 
                                SID == params$stand_id)
  health_st    <- dplyr::filter(params$health_summary, 
                                SID == params$stand_id) 


} else if("Site_ID" %in% colnames(params$stand_polys)) {
  # FMG Site
  age_pts_st   <- dplyr::filter(params$age_pts, 
                                Site_ID == params$stand_id)
  fixed_pts_st <- dplyr::filter(params$fixed_pts, 
                                Site_ID == params$stand_id)
  prism_pts_st <- dplyr::filter(params$prism_pts, 
                                Site_ID == params$stand_id)
  age_fixed_st <- dplyr::filter(params$age_fixed_summary, 
                                Site_ID == params$stand_id)
  stand_st     <- dplyr::filter(params$stand_summary, 
                                Site_ID == params$stand_id)
  species_st   <- dplyr::filter(params$species_summary, 
                                Site_ID == params$stand_id)
  health_st    <- dplyr::filter(params$health_summary, 
                                Site_ID == params$stand_id) 

} else {
  stop("`stand_polys` is missing a known FMG ID field.")
}
```

```{r site_or_stand, echo=FALSE}
# Determine if `stand_polys` are `Site` or `Stand`, then calculate acres
if("SID" %in% colnames(params$stand_polys)) {
  # FMG Stand
  poly_st <- dplyr::filter(params$stand_polys,
                           SID == params$stand_id)
  area <- sf::st_area(poly_st)
  acres <- units::set_units(area, acre)

} else if("Site_ID" %in% colnames(params$stand_polys)) {
  # FMG Site
  poly_st <- dplyr::filter(params$stand_polys,
                           Site_ID == params$stand_id)
  area <- sf::st_area(poly_st)
  acres <- units::set_units(area, acre)

} else {
  stop("`stand_polys` is missing a known FMG ID field.")
}
```

```{r sort_tables, echo=FALSE}
# Sort tables
species_sort <- dplyr::arrange(species_st, desc(AV_BA), desc(AV_TPA), desc(QM_DBH))
health_sort <- dplyr::arrange(health_st, desc(AV_TPA))
```

```{r set_factors, echo=FALSE}
# Set health_summary$TR_HLTH labels
health_sort$TR_HLTH <- factor(health_sort$TR_HLTH,
                              levels = c("V", "S", "SD", "D"),
                              labels = c("Healthy-Vigorous", "Stressed", 
                                         "Significant Decline", "Dead"))
```

```{r hard_mast, echo=FALSE}
# Calculate hard mast stats
## Get list of hard mast species
hard_mast_spp <- dplyr::filter(spp_masttype, MAST_TYPE == "HARD")

## Filter species_st for only hard mast species
species_hard_mast <- dplyr::filter(species_st, TR_SP %in% hard_mast_spp$TR_SP)

# Calculate hard mast tpa sum 
hard_mast_tpa_sum <- sum(species_hard_mast$AV_TPA)

# Calculate hard mast ba sum
hard_mast_ba_sum <- sum(species_hard_mast$AV_BA)

# Calculate hard mast QM_DBH
hard_mast_BA_TPA <- (hard_mast_ba_sum/hard_mast_tpa_sum)
hard_mast_QM_DBH <- sqrt(hard_mast_BA_TPA/0.005454154)

# Count of hard mast species
hard_mast_spp_count <- length(species_hard_mast$TR_SP)

# Filter age_pts_st for only hard mast species
age_hard_mast <- dplyr::filter(age_pts_st, AGE_SP %in% hard_mast_spp$TR_SP)
```

```{r stocking, echo=FALSE}
# Set stocking parameters (Larsen et al., 2010)
amd_p1 <- 0.259
amd_p2 <- 0.973

a_line_p1 <- 0.0685724
a_line_p2 <- 0.0010125
a_line_p3 <- 0.0023656

# QMD to AMD conversion
amd <- amd_p1 + (amd_p2 * stand_st$QM_DBH)

# Calculate stocking
stocking <- stand_st$AV_TPA * 
            (a_line_p1 + a_line_p2 * amd + a_line_p3 * stand_st$QM_DBH^2)

stocking_pct <- paste0(round(stocking, 0), "%")
stocking_pct <- ifelse(stocking < 10, "<10%", stocking_pct)
stocking_pct <- ifelse(stocking > 110, ">110%", stocking_pct)

# Calculate hard mast stocking
hm_stocking <- hard_mast_tpa_sum *
               (a_line_p1 + a_line_p2 * amd + a_line_p3 * hard_mast_QM_DBH^2)

hm_stocking_pct <- paste0(round(hm_stocking, 0), "%")
hm_stocking_pct <- ifelse(hm_stocking < 10, "<10%", hm_stocking_pct)
hm_stocking_pct <- ifelse(hm_stocking > 110, ">110%", hm_stocking_pct)

```

```{r parse_fmg_levels, echo=FALSE}
# Parse FMG spatial hierarchy
## Clean up `Site_ID` to make it easier to parse
SITE_CLEAN <- str_replace(stand_st$Site_ID, "st", "t")

# Determine if `stand_st` are `Site` or `Stand`, then Parse FMG spatial hierarchy
## Clean up `SID` or `Site_ID` to make it easier to parse
if("SID" %in% colnames(stand_st)) {
  # FMG Stand
  SITE_CLEAN <- str_replace(stand_st$SID, "st", "t")

} else if("Site_ID" %in% colnames(stand_st)) {
  # FMG Site
  SITE_CLEAN <- str_replace(stand_st$Site_ID, "st", "t")

} else {
  stop("`stand_st` is missing a known FMG ID field.")
}

## Match alpha hierarchy delimiter (p, c, u, t, s), then digits, 0 or more (\\d*)
pool_label  <- stringr::str_match(SITE_CLEAN, "p\\d*")[1]
comp_label  <- stringr::str_match(SITE_CLEAN, "c\\d*")[1]
unit_label  <- stringr::str_match(SITE_CLEAN, "u\\d*")[1]
site_label  <- stringr::str_match(SITE_CLEAN, "t\\d*")[1]
stand_label <- stringr::str_match(SITE_CLEAN, "s\\d*")[1]
```

```{r species_richness, echo=FALSE}
# Calculate species richness
## Typical Species
## Get list of 'typical' species
typical_spp <- dplyr::filter(spp_masttype, TYPICAL == "COMMON")

## Filter species_st for only 'typical' species
species_typical <- dplyr::filter(species_st, TR_SP %in% typical_spp$TR_SP)

## Count 'typical' species
typical_spp_count <- length(species_typical$TR_SP)

## Other Species
## Get list of 'other' species
other_spp <- dplyr::filter(spp_masttype, MAST_TYPE != "HARD",
                                         TYPICAL != "COMMON")
## Filter species_st for only 'other' species
species_other <- dplyr::filter(species_st, TR_SP %in% other_spp$TR_SP)

## Count 'typical' species
other_spp_count <- length(species_other$TR_SP)

## Create "Species Richness" string
species_richness <- paste0(hard_mast_spp_count, other_spp_count, typical_spp_count)
```

```{r understory, echo=FALSE, warning=FALSE, message=FALSE}
# Simplify fixed_pts_st to just understory species fields
fixed_understory <- fixed_pts_st[, c("PL_NUM", "UND_SP1", "UND_SP2", "UND_SP3")]
# Drop factors
fixed_understory$UND_SP1 <- as.character(fixed_understory$UND_SP1)
fixed_understory$UND_SP2 <- as.character(fixed_understory$UND_SP2)
fixed_understory$UND_SP3 <- as.character(fixed_understory$UND_SP3)
# Drop geometry
fixed_understory <- sf::st_drop_geometry(fixed_understory)
# Set missing data to NA
fixed_understory <- set_na(fixed_understory)
# Convert to long format by combining `UND_SP*` fields into a single field
understory <- tidyr::pivot_longer(data = fixed_understory,
                                  cols = -PL_NUM,
                                  names_to = c(".value", "SP"),
                                  names_sep = "_",
                                  values_drop_na = TRUE)
# Group by understory species
understory_species <- dplyr::group_by(understory, UND)
# Count understory species
understory_species_count <- dplyr::summarize(understory_species, 
                                             count = n())
# Sort 
understory_species_count <- dplyr::arrange(understory_species_count, desc(count))
```

```{r ground, echo=FALSE, warning=FALSE, message=FALSE}
# Simplify fixed_pts_st to just ground species fields
fixed_ground <- fixed_pts_st[, c("PL_NUM", "GRD_SP1", "GRD_SP2", "GRD_SP3")]
# Drop factors
fixed_ground$GRD_SP1 <- as.character(fixed_ground$GRD_SP1)
fixed_ground$GRD_SP2 <- as.character(fixed_ground$GRD_SP2)
fixed_ground$GRD_SP3 <- as.character(fixed_ground$GRD_SP3)
# Drop geometry
fixed_ground <- sf::st_drop_geometry(fixed_ground)
# Set missing data to NA
fixed_ground <- set_na(fixed_ground)
# Convert to long format by combining `GRD_SP*` fields into a single field
ground <- tidyr::pivot_longer(data = fixed_ground,
                              cols = -PL_NUM,
                              names_to = c(".value", "SP"),
                              names_sep = "_",
                              values_drop_na = TRUE)
# Group by understory species
ground_species <- dplyr::group_by(ground, GRD)
# Count understory species
ground_species_count <- dplyr::summarize(ground_species, 
                                         count = n())
# Sort 
ground_species_count <- dplyr::arrange(ground_species_count, desc(count))
```

```{r set_variables, echo=FALSE}
# collector
forester <- ""
date <- ""

# stand_id
pool           <- pool_label
compartment    <- comp_label
unit           <- unit_label
site           <- site_label
stand          <- stand_label
num_plots      <- stand_st$NUM_PL
num_age_plots  <- length(age_pts_st$PLOT)
walk_acres     <- round(acres, 0)
inventory_year <- unique(lubridate::year(fixed_pts_st$FP_DATE))
dom_soil_type  <- NA                                  # new tool will calculate

# stand-summary-data
tpa              <- ifelse(stand_st$AV_TPA > 0 & stand_st$AV_TPA < 1, "<1", 
                           floor(stand_st$AV_TPA))
basal_area       <- ifelse(stand_st$AV_BA > 0 & stand_st$AV_BA < 1, "<1", 
                           floor(stand_st$AV_BA))
qm_dbh           <- paste0(floor(stand_st$QM_DBH), '"')
stocking         <- stocking_pct
canopy_height    <- paste0(round(age_fixed_st$OV_HT/5)*5, "'")    # nearest 5 ft
canopy_closure   <- paste0(round(age_fixed_st$OV_CLSR, -1), "%")  # nearest 10 %
hard_mast_tpa    <- dplyr::if_else(hard_mast_tpa_sum > 0 & hard_mast_tpa_sum < 1,
                                   "<1", 
                                   as.character(floor(hard_mast_tpa_sum)), "0")
hard_mast_ba     <- dplyr::if_else(hard_mast_ba_sum > 0 & hard_mast_ba_sum < 1,
                                   "<1", 
                                   as.character(floor(hard_mast_ba_sum)), "0")
hard_mast_qm_dbh <- paste0(floor(hard_mast_QM_DBH), '"')
hard_mast_stock  <- hm_stocking_pct                    
under_height     <- paste0(round(age_fixed_st$UND_HT, 0), "'")
snag_tpa         <- ifelse(stand_st$SNAG_TPA > 0 & stand_st$SNAG_TPA < 1, "<1",                                floor(stand_st$SNAG_TPA))
stand_age        <- floor(age_fixed_st$TR_AGE)
hard_mast_age    <- mean(age_hard_mast$AGE_ORIG)
growth           <- floor(mean(age_pts_st$AGE_GRW))
stand_health     <- health_sort[1,]$TR_HLTH
species_rich     <- species_richness
regen_rate       <- ifelse(age_fixed_st$UND_COV > 0 & age_fixed_st$UND_COV < 1,
                           "<1", floor(age_fixed_st$UND_COV))

# Size Class
sapling_tpa      <- NA                                    # added in the future
polesize_tpa     <- floor(stand_st$POL_TPA)
sawtimber_tpa    <- floor(stand_st$SAW_TPA)
mature_tpa       <- floor(stand_st$MAT_TPA)
overmature_tpa   <- floor(stand_st$OVM_TPA)
sapling_ba       <- NA                                    # added in the future
polesize_ba      <- NA                                    # added in the future
sawtimber_ba     <- NA                                    # added in the future
mature_ba        <- NA                                    # added in the future
overmature_ba    <- NA                                    # added in the future

# Top 3 Understory Species
under_species_1 <- understory_species_count$UND[1]
under_species_2 <- understory_species_count$UND[2]
under_species_3 <- understory_species_count$UND[3]

# Top 3 Ground Species
ground_species_1 <- ground_species_count$GRD[1]
ground_species_2 <- ground_species_count$GRD[2]
ground_species_3 <- ground_species_count$GRD[3]

# Top 5 Overstory Species
o1_usda_code  <- species_sort[1,]$TR_SP
o1_avg_tpa    <- ifelse(species_sort[1,]$AV_TPA > 0 & species_sort[1,]$AV_TPA < 1,
                           "<1", floor(species_sort[1,]$AV_TPA))
o1_avg_ba     <- ifelse(species_sort[1,]$AV_BA > 0 & species_sort[1,]$AV_BA < 1,
                           "<1", floor(species_sort[1,]$AV_BA))
o1_qm_dbh     <- paste0(floor(species_sort[1,]$QM_DBH), '"')
o1_target_tpa <- ""                         
o1_target_ba  <- ""

o2_usda_code  <- species_sort[2,]$TR_SP
o2_avg_tpa    <- ifelse(species_sort[2,]$AV_TPA > 0 & species_sort[2,]$AV_TPA < 1,
                           "<1", floor(species_sort[2,]$AV_TPA))
o2_avg_ba     <- ifelse(species_sort[2,]$AV_BA > 0 & species_sort[2,]$AV_BA < 1,
                           "<1", floor(species_sort[2,]$AV_BA))
o2_qm_dbh     <- paste0(floor(species_sort[2,]$QM_DBH), '"')
o2_target_tpa <- ""
o2_target_ba  <- ""

o3_usda_code  <- species_sort[3,]$TR_SP
o3_avg_tpa    <- ifelse(species_sort[3,]$AV_TPA > 0 & species_sort[3,]$AV_TPA < 1,
                           "<1", floor(species_sort[3,]$AV_TPA))
o3_avg_ba     <- ifelse(species_sort[3,]$AV_BA > 0 & species_sort[3,]$AV_BA < 1,
                           "<1", floor(species_sort[3,]$AV_BA))
o3_qm_dbh     <- paste0(floor(species_sort[3,]$QM_DBH), '"')
o3_target_tpa <- ""
o3_target_ba  <- ""

o4_usda_code  <- species_sort[4,]$TR_SP
o4_avg_tpa    <- ifelse(species_sort[4,]$AV_TPA > 0 & species_sort[4,]$AV_TPA < 1,
                           "<1", floor(species_sort[4,]$AV_TPA))
o4_avg_ba     <- ifelse(species_sort[4,]$AV_BA > 0 & species_sort[4,]$AV_BA < 1,
                           "<1", floor(species_sort[4,]$AV_BA))
o4_qm_dbh     <- paste0(floor(species_sort[4,]$QM_DBH), '"')
o4_target_tpa <- ""
o4_target_ba  <- ""

o5_usda_code  <- species_sort[5,]$TR_SP
o5_avg_tpa    <- ifelse(species_sort[5,]$AV_TPA > 0 & species_sort[5,]$AV_TPA < 1,
                           "<1", floor(species_sort[5,]$AV_TPA))
o5_avg_ba     <- ifelse(species_sort[5,]$AV_BA > 0 & species_sort[5,]$AV_BA < 1,
                           "<1", floor(species_sort[5,]$AV_BA))
o5_qm_dbh     <- paste0(floor(species_sort[5,]$QM_DBH),'"')
o5_target_tpa <- ""
o5_target_ba  <- ""
```

<!--
## Stand ID
-->

::::: {#collector .grid-5w-1h }
::: {.var-name}
Forester
:::
::: {.empty-box}
`r forester`
:::
::: {.var-name}
Date
:::
::: {.empty-box}
`r date`
:::
:::::

::::: {#stand_id_1 .grid-5w-2h}
::: {.var-name}
FMG Pool
:::
::: {.var-value}
`r pool`
:::
::: {.var-name}
FMG Compartment
:::
::: {.var-value}
`r compartment`
:::
::: {.var-name}
FMG Unit
:::
::: {.var-value}
`r unit`
:::
::: {.var-name}
FMG Site 
:::
::: {.var-value}
`r site`
:::
::: {.var-name}
FMG Stand 
:::
::: {.var-value}
`r stand`
:::
:::::

::::: {#stand_id_2 .grid-5w-2h}
::: {.var-name}
\# of Plots
:::
::: {.var-value}
`r num_plots`
:::
::: {.var-name}
\# Age Plots
:::
::: {.var-value}
`r num_age_plots`
:::
::: {.var-name}
Area (acre)
:::
::: {.var-value}
`r walk_acres`
:::
::: {.var-name}
Inventory Year
:::
::: {.var-value}
`r inventory_year`
:::
::: {.var-name}
Dominant Soil Type
:::
::: {.var-value}
`r dom_soil_type`
:::
:::::



## Stand Summary Data

::::: {#stand-summary-data .grid-6w-6h}
::: {.var-name}
Trees per Acre
:::
::: {.var-value}
`r tpa`
:::
::: {.var-name}
Hard Mast TPA
:::
::: {.var-value}
`r hard_mast_tpa`
:::
::: {.var-name}
Stand Age
:::
::: {.var-value}
`r stand_age`
:::
::: {.var-name}
Basal Area
:::
::: {.var-value}
`r basal_area`
:::
::: {.var-name}
Hard Mast BA
:::
::: {.var-value}
`r hard_mast_ba`
:::
::: {.var-name}
Hard Mast Age
:::
::: {.var-value}
`r hard_mast_age`
:::
::: {.var-name}
QM DBH
:::
::: {.var-value}
`r qm_dbh`
:::
::: {.var-name}
Hard Mast QM DBH
:::
::: {.var-value}
`r hard_mast_qm_dbh`
:::
::: {.var-name}
Growth
:::
::: {.var-value}
`r growth`
:::
::: {.var-name}
Stocking
:::
::: {.var-value}
`r stocking`
:::
::: {.var-name}
Hard Mast Stocking
:::
::: {.var-value}
`r hard_mast_stock`
:::
::: {.var-name}
Stand Health
:::
::: {.var-value}
`r stand_health`
:::
::: {.var-name}
Canopy Height
:::
::: {.var-value}
`r canopy_height`
:::
::: {.var-name}
Understory Height
:::
::: {.var-value}
`r under_height`
:::
::: {.var-name}
Species Richness
:::
::: {.var-value}
`r species_rich`
:::
::: {.var-name}
Canopy Closure
::: 
::: {.var-value}
`r canopy_closure`
:::
::: {.var-name}
Snag TPA
:::
::: {.var-value}
`r snag_tpa`
:::
::: {.var-name}
Regeneration Rate
:::
::: {.var-value}
`r regen_rate`
:::
:::::


<!--
## Section 3
-->

:::::::::::: {#section-3 .group-3-horz}

:::::::: {.section-box}
## Size Class
::::: {.grid-3w-6h}
::: {.var-name}
Class
:::
::: {.var-name}
TPA
:::
::: {.var-name}
BA
:::
::: {.var-name}
Sapling (1"-5")
:::
::: {.var-value}
`r sapling_tpa`
:::
::: {.var-value}
`r sapling_ba`
:::
::: {.var-name}
Polesize (5"-12")
:::
::: {.var-value}
`r polesize_tpa`
:::
::: {.var-value}
`r polesize_ba`
:::
::: {.var-name}
Sawtimber (12"-18")
:::
::: {.var-value}
`r sawtimber_tpa`
:::
::: {.var-value}
`r sawtimber_ba`
:::
::: {.var-name}
Mature (18"-24")
:::
::: {.var-value}
`r mature_tpa`
:::
::: {.var-value}
`r mature_ba`
:::
::: {.var-name}
Overmature (24"+)
:::
::: {.var-value}
`r overmature_tpa`
:::
::: {.var-value}
`r overmature_ba`
:::
:::::
::::::::

:::::::: {.section-box}
## Top 3 Understory
::::: {.grid-2w-4h}
::: {.var-name}
Species 1
:::
::: {.var-value}
`r under_species_1`
:::
::: {.var-name}
Species 2
:::
::: {.var-value}
`r under_species_2`
:::
::: {.var-name}
Species 3
:::
::: {.var-value}
`r under_species_3`
:::
:::::
::::::::

:::::::: {.section-box}
## Top 3 Ground
::::: {.grid-2w-4h}
::: {.var-name}
Species 1
:::
::: {.var-value}
`r ground_species_1`
:::
::: {.var-name}
Species 2
:::
::: {.var-value}
`r ground_species_2`
:::
::: {.var-name}
Species 3
:::
::: {.var-value}
`r ground_species_3`
:::
:::::
::::::::
::::::::::::



<!--
## Section 4
-->

:::::::::::: {#section-4 .group-5-vert}
## Top 5 Overstory

<!-- Overstory Species 1 -->
:::::::: {.section-box}
::::: {.grid-6w-2h}
::: {.var-name}
USDA Code
:::
::: {.var-value}
`r o1_usda_code`
:::
::: {.var-name}
Avg. TPA
:::
::: {.var-value}
`r o1_avg_tpa`
:::
::: {.var-name}
Avg. BA
:::
::: {.var-value}
`r o1_avg_ba`
:::
::: {.var-name}
QM DBH
:::
::: {.var-value}
`r o1_qm_dbh`
:::
::: {.var-name}
Target TPA
:::
::: {.var-value}
`r o1_target_tpa`
:::
::: {.var-name}
Target BA
:::
::: {.var-value}
`r o1_target_ba`
:::
:::::
::::::::

<!-- Overstory Species 2 -->
:::::::: {.section-box}
::::: {.grid-6w-2h}
::: {.var-name}
USDA Code
:::
::: {.var-value}
`r o2_usda_code`
:::
::: {.var-name}
Avg. TPA
:::
::: {.var-value}
`r o2_avg_tpa`
:::
::: {.var-name}
Avg. BA
:::
::: {.var-value}
`r o2_avg_ba`
:::
::: {.var-name}
QM DBH
:::
::: {.var-value}
`r o2_qm_dbh`
:::
::: {.var-name}
Target TPA
:::
::: {.var-value}
`r o2_target_tpa`
:::
::: {.var-name}
Target BA
:::
::: {.var-value}
`r o2_target_ba`
:::
:::::
::::::::

<!-- Overstory Species 3 -->
:::::::: {.section-box}
::::: {.grid-6w-2h}
::: {.var-name}
USDA Code
:::
::: {.var-value}
`r o3_usda_code`
:::
::: {.var-name}
Avg. TPA
:::
::: {.var-value}
`r o3_avg_tpa`
:::
::: {.var-name}
Avg. BA
:::
::: {.var-value}
`r o3_avg_ba`
:::
::: {.var-name}
QM DBH
:::
::: {.var-value}
`r o3_qm_dbh`
:::
::: {.var-name}
Target TPA
:::
::: {.var-value}
`r o3_target_tpa`
:::
::: {.var-name}
Target BA
:::
::: {.var-value}
`r o3_target_ba`
:::
:::::
::::::::

<!-- Overstory Species 4 -->
:::::::: {.section-box}
::::: {.grid-6w-2h}
::: {.var-name}
USDA Code
:::
::: {.var-value}
`r o4_usda_code`
:::
::: {.var-name}
Avg. TPA
:::
::: {.var-value}
`r o4_avg_tpa`
:::
::: {.var-name}
Avg. BA
:::
::: {.var-value}
`r o4_avg_ba`
:::
::: {.var-name}
QM DBH
:::
::: {.var-value}
`r o4_qm_dbh`
:::
::: {.var-name}
Target TPA
:::
::: {.var-value}
`r o4_target_tpa`
:::
::: {.var-name}
Target BA
:::
::: {.var-value}
`r o4_target_ba`
:::
:::::
::::::::

<!-- Overstory Species 5 -->
:::::::: {.section-box}
::::: {.grid-6w-2h}
::: {.var-name}
USDA Code
:::
::: {.var-value}
`r o5_usda_code`
:::
::: {.var-name}
Avg. TPA
:::
::: {.var-value}
`r o5_avg_tpa`
:::
::: {.var-name}
Avg. BA
:::
::: {.var-value}
`r o5_avg_ba`
:::
::: {.var-name}
QM DBH
:::
::: {.var-value}
`r o5_qm_dbh`
:::
::: {.var-name}
Target TPA
:::
::: {.var-value}
`r o5_target_tpa`
:::
::: {.var-name}
Target BA
:::
::: {.var-value}
`r o5_target_ba`
:::
:::::
::::::::

::::::::::::

report version: `r report_version`